Jack Antonoff-ification of pop music

### 2023-04-04 outputs/paper/paper.qmd
removed the warnings from the render

```{r}
#| label: fig-energy
#| fig-cap: Energy Variable
#| echo: false

@@

```{r}
#| label: fig-danceability
#| fig-cap: Danceability Variable
#| echo: false

@@

```{r}
#| label: fig-valence
#| fig-cap: Valence Variable
#| echo: false

@@

```{r}
#| label: fig-acousticness
#| fig-cap: Acousticness Variable
#| echo: false

@@

```{r}
#| label: fig-instrumentalness
#| fig-cap: Instrumentalness Variable
#| echo: false

@@

#| label: fig-temp
#| fig-cap: Tempo Variable
#| echo: false

>>>>

```{r}
#| label: fig-energy
#| fig-cap: Energy Variable
#| echo: false
#| warning: false

@@

```{r}
#| label: fig-danceability
#| fig-cap: Danceability Variable
#| echo: false
#| warning: false

@@

```{r}
#| label: fig-valence
#| fig-cap: Valence Variable
#| echo: false
#| warning: false

@@

```{r}
#| label: fig-acousticness
#| fig-cap: Acousticness Variable
#| echo: false
#| warning: false

@@

```{r}
#| label: fig-instrumentalness
#| fig-cap: Instrumentalness Variable
#| echo: false
#| warning: false

@@

#| label: fig-temp
#| fig-cap: Tempo Variable
#| echo: false
#| warning: false
